### 2013-11-20 finalPlots.Rmd

% Final graphics for the paper

- [back to index](index.html)

`generated at:`
```{r, echo=FALSE}
Sys.time()
```
---

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(kaRski)
knit("finalPlots.Rmd")
system("pandoc -s finalPlots.md -o finalPlots.html --toc --number-section")

@@

```{rattribFinalPlotsLoad}
library(ggplot2)
library(gridExtra)
library(plyr)
library(grid)
#########################################
#########################################
setwd("~/workspace/lits/attrib/attrib_year2013")
#########################################
cbPalette <- c("#E69F00","#56B4E9","#999999","#009E73", "#F0E442", "#0072B2","#D55E00", "#CC79A7")

@@

```{rattribFinalPlotsGDP}
# valitaan vaan kohdemaat #
t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpchange07.10) ~ COR, data=t4, mean),2)

@@

>>>>

# Final graphics for the paper

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit2html('finalPlots.Rmd', options = c('toc', markdown::markdownHTMLOptions(TRUE)))

@@

```{rattribFinalPlotsLoad}
library(ggplot2)
library(gridExtra)
library(plyr)
library(grid)
#########################################
#########################################
setwd("~/workspace/lits/attributions")
#########################################
cbPalette <- c("#E69F00","#56B4E9","#999999","#009E73", "#F0E442", "#0072B2","#D55E00", "#CC79A7")

@@

```{rattribFinalPlotsGDP}

# valitaan vaan kohdemaat #
t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpchange07.10) ~ COR, data=t4, mean),2)

@@

## Perceived inequality from data

```{rattribFinalPlotsPG}

# Perceived inequality from data

func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$perGini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, perGini) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=perGini, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(perGini,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x = "Perceived inequality from data", 
       y = "Support for social blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=perGini, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=perGini, 
                            y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=perGini, 
                           y=socialBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  #coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

func <- function(t3)
{
  return(data.frame(COR = cor(t3$individualBlame, t3$perGini)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(individualBlame, perGini) ~ COR, data=t4, mean),2)
plot2 <- ggplot(t4, aes(x=perGini, 
                        y=individualBlame, label=cntry)) +
geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_text(data=cnames, aes(perGini,individualBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  labs(x ="Perceived inequality from data", 
       y = "Support for individual blame type of explanation (%)") +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=perGini, 
                          y=individualBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=perGini, 
                            y=individualBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=perGini, 
                           y=individualBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  scale_colour_manual(values=cbPalette) +
  #coord_cartesian(xlim=c(-2,2)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

pdf("figure/scatter_perGini.pdf", width=12/2.54, height=18/2.54)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

ppi <- 300
png("figure/scatter_perGini.png", width=12/2.54*ppi, height=18/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

png("figure/scatter_perGiniSB.png", width=12/2.54*ppi, height=8/2.54*ppi, res=ppi)
plot1
dev.off()
png("figure/scatter_perGiniIB.png", width=12/2.54*ppi, height=8/2.54*ppi, res=ppi)
plot2
dev.off()

![](figure/scatter_perGini.png)

### 2013-11-20 regressionModelling.Rmd

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit2html('regressionModelling.Rmd', options = c('toc', markdown::markdownHTMLOptions(TRUE)))

>>>>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit2html('regressionModelling.Rmd', options = c('toc', markdown::markdownHTMLOptions(TRUE)))
```
